---
title: "TOP 10 MOST POPULOUS CITIES"
author: "James Ottavi"
date: "1/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggmap)
require(leaflet)
```

# Size and Location

This analysis looks at two items:
1. Where are the largest cities in the world?
2. What is there approximate size?

This analysis takes the data from the below link. Map was created in combination with the leaflet and ggmap packages of R
<http://www.worldatlas.com/citypops.htm>.

## Step 1: Get Data
The data taken from the above link was loaded into a data frame called *df*.
```{r init, message=FALSE}
cities <- c("TOKYO", "JAKARTA", "DELHI", "MANILA", "SEOUL", "SHANGHAI", "KARACHI",
            "BEIJING", "NEW YORK CITY", "GUANGZHAO")
colors <- c(rep("RED", 8), "BLUE", "RED")
pop <- c(37.8, 30.5, 25.0, 24.1, 23.5, 23.4, 22.1, 21.0, 20.6, 20.6) * 1000000
df <- data.frame(city = cities, color = colors, population = pop, 
                 geocode(cities))
```

## Step 2: Create Interactive Map
The above data is recreated in a world map using the leaflet and ggmap packages.

```{r map, echo=FALSE, message=FALSE}
map <- df %>% leaflet() %>% addTiles %>% 
  addCircles(radius = (df$population)/25, weight = .5, color = df$color, 
             popup= paste0(df$city, " (",df$population, ")"))
map
```
